DATA 621---Business Analytics and Data Mining

### 2020-09-10 HW1/HW1_AF.Rmd
more grammar updates

We are given a data set containing 2,276 records, each of which includes 15 statistics
and the total number of wins a team had in a given year. On average, the team wins about 
50% of the games they play (81 games out of 162), with the best season having 146 wins 
and the worst season having 0 wins. The data is normally distributed and most seasons have 
between 49 and 112 wins (blue lines below). This means that there aren't too many extreme 
seasons where the team won significantly more or significantly less games than usual. This 
serves as a good gut-check for our final predictions; if the predicted wins are too high or 
too low, we know something is probably off.

>>>>

We are given a data set containing 2,276 records, each of which includes 15 statistics
and the total number of wins a team had in a given year. On average, about 50% of games 
played are won (81 games out of 162), with the best season having 146 wins and the worst 
season having 0 wins. The data is normally distributed and most years have between 49 
and 112 wins (blue lines below). The nature of the distribution means there aren't too 
many extreme seasons where wins are significantly higher or lower than usual. This serves 
as a good gut-check for our final predictions; if the predicted wins are too high or too 
low, we know something in our model is probably off.
